---
title: "Thinking Hats Study Graphs"
output: html_notebook
---

```{r}
#required libraries
library(ggplot2)
library(car)
library(dplyr)
library(reshape2)
library(pwr)
library(irr)
library(coin)
```
```{r}
baseline <- read.table("study1/baseline_data.csv", sep=",", header=TRUE)
order <- read.table("study2/order_study_data.csv", sep=",", header=TRUE)
```

---BASELINE STUDY---
```{r}
#summary of data
baseline <- group_by(baseline, condition)
baseline_summary <- summarise(baseline,
                              orig = mean(final_orig),
                              sd_orig = sd(final_orig),
                              se_orig = sd_orig/sqrt(length(condition)),
                              util = mean(final_prac),
                              sd_util = sd(final_prac),
                              se_util = sd_util/sqrt(length(condition)),
                              diff = mean(difference),
                              sd_diff = sd(difference),
                              se_diff = sd_diff/sqrt(length(condition)))

baseline_summary
```
Comparison of average originality scores for both conditions
```{r}
ggplot(baseline_summary, aes(x=condition, y=orig, fill=condition)) +
  geom_bar(stat="identity", position=position_dodge()) +
  geom_errorbar(aes(ymin=orig-se_orig, ymax=orig+se_orig), width=.2) +
  scale_fill_manual(breaks=c("Exploit","Explore"),values= c("darkblue","darkgreen")) +
  scale_y_continuous(name="Average Rating",limits=c(0,4)) +
  theme_bw()

#significance test
independence_test(condition ~ final_orig, data = baseline)
```
Originality ratings are significantly different between conditions. Comparison of utility ratings
```{r}
ggplot(baseline_summary, aes(x=condition, y=util, fill=condition)) +
  geom_bar(stat="identity", position=position_dodge()) +
  geom_errorbar(aes(ymin=util-se_util, ymax=util+se_util), width=.2) +
  scale_fill_manual(breaks=c("Exploit","Explore"),values= c("darkblue","darkgreen")) +
  scale_y_continuous(name="Average Rating",limits=c(0,4)) +
  theme_bw()

#significance test
independence_test(condition ~ final_prac, data = baseline)
```
No significant difference in utility ratings between conditions.

```{r}
#histogram of originality ratings
ggplot(baseline, aes(x=final_orig,fill=condition,color=condition))+
  geom_histogram(alpha=0.5, position="dodge", binwidth=.5) +
  scale_color_manual(values=c("darkblue","darkgreen")) +
  scale_fill_manual(values=c("darkblue","darkgreen")) +
  labs(x="Originality Ratings") +
  theme_bw()

#histogram of utility ratings
ggplot(baseline, aes(x=final_prac,fill=condition,color=condition))+
  geom_histogram(alpha=0.5, position="dodge", binwidth=.5) +
  scale_color_manual(values=c("darkblue","darkgreen")) +
  scale_fill_manual(values=c("darkblue","darkgreen")) +
  labs(x="Utility Ratings") +
  theme_bw()
```
Baseline study results: Explore condition designs received significantly higher originality ratings while there were no significant differences in utility ratings.

---ORDER STUDY---
```{r}
order <- group_by(order, condition)
aggregate <- summarise(order,
                       n = length(condition),
                         #mean ratings
                       med_total_orig = median(sum_orig),   
                       avg_total_orig = mean(sum_orig),
                          sd_total_orig = sd(sum_orig),
                          se_total_orig = sd_total_orig/sqrt(length(condition)),
                      med_avg_orig = median(sum_orig),   
                       avg_orig = mean(orig),
                          sd_avg_orig = sd(orig),
                          se_avg_orig = sd_avg_orig/sqrt(length(condition)),
                       med_total_util = median(sum_util),
                          avg_total_util = mean(sum_util),
                          sd_total_util = sd(sum_util),
                          se_total_util = sd_total_util/sqrt(length(condition)),
                       med_avg_util = median(util),   
                       avg_util = mean(util),
                          sd_avg_util = sd(util),
                          se_avg_util = sd_avg_util/sqrt(length(condition)),
                      sum = mean(sum_total),
                      sd_sum = sd(sum_total),
                      se_sum = sd_sum/sqrt(length(condition)))

aggregate

```
Comparing originality and utility rating distributions between conditions for first design
```{r}

ggplot(order, aes(x=orig_t1, fill=condition,color=condition))+
  geom_histogram(alpha=0.5, position="dodge", binwidth=.5) +
  scale_color_manual(values=c("darkblue","darkgreen")) +
  scale_fill_manual(values=c("darkblue","darkgreen")) +
  labs(x="First Design Originality Ratings") +
  theme_bw()

#histogram of utility ratings
ggplot(order, aes(x=util_t1,fill=condition,color=condition))+
  geom_histogram(alpha=0.5, position="dodge", binwidth=.5) +
  scale_color_manual(values=c("darkblue","darkgreen")) +
  scale_fill_manual(values=c("darkblue","darkgreen")) +
  labs(x="First Design Utility Ratings") +
  theme_bw()
```
Comparing originality and utility rating distributions between conditions for second design
```{r}

ggplot(order, aes(x=orig_t2,fill=condition,color=condition))+
  geom_histogram(alpha=0.5, position="dodge", binwidth=.5) +
  scale_color_manual(values=c("darkblue","darkgreen")) +
  scale_fill_manual(values=c("darkblue","darkgreen")) +
  labs(x="Second Design Originality Ratings") +
  theme_bw()

#histogram of utility ratings
ggplot(order, aes(x=util_t2,fill=condition,color=condition))+
  geom_histogram(alpha=0.5, position="dodge", binwidth=.5) +
  scale_color_manual(values=c("darkblue","darkgreen")) +
  scale_fill_manual(values=c("darkblue","darkgreen")) +
  labs(x="Second Design Utility Ratings") +
  theme_bw()
```
Comparing histogram of sum scores for first and second designs
```{r}
#first design
ggplot(order, aes(x=sum_t1,fill=condition,color=condition))+
  geom_histogram(alpha=0.5, position="dodge", binwidth=.5) +
  scale_color_manual(values=c("darkblue","darkgreen")) +
  scale_fill_manual(values=c("darkblue","darkgreen")) +
  labs(x="First Design Sum Ratings") +
  theme_bw()

#second design
ggplot(order, aes(x=sum_t2,fill=condition,color=condition))+
  geom_histogram(alpha=0.5, position="dodge", binwidth=.5) +
  scale_color_manual(values=c("darkblue","darkgreen")) +
  scale_fill_manual(values=c("darkblue","darkgreen")) +
  labs(x="Second Design Sum Ratings") +
  theme_bw()
```

